%Rope
\subsection{Rope}

Rope is a python refactoring tool written in Python, which works like a python library, it is necessary to import it to the your program, and add the project correctly.
In order to make it easier Rope makes some assumptions about a python program, it assumes that it only has assignments and functions calls %(can this be a bad thing?)
for the assignments it is simple, because `PyName` objects can handle that. However for functions calls it is necessary to have other approaches in order to obtain the necessary information. 

It uses a Static Object Analysis which analyses the modules or scope to get information about functions. It only analysis the scopes when they changed and only analyses the modules when asked by the user because this approach is time consuming. The other approach is the Dynamic Object Analysis that starts working when a module is running, then it collects information about parameters passed to and returned from functions in order to get all the information needed. The main problem with this approach is that this it is slow while collecting information however it isn't slow while accessing the information.

It stores the information in a `objectdb.ObjectDB`. If it needs the information, and there is nothing on the ObjectDB the Static object inference starts trying to infer the object that is returned from it.

Rope uses an AST in order to store the syntax information about the programs.

It was implement simple refactoring operations such as:
	Rename (functions, modules)
	Extract method/local variable
	Move class/function/module/package/method
	inline method/local variable/parameter
	Restructuring (like converting "${a}.f(${b})" to "${b}.g(${a})" where "a: type=mymod.A") 
	Introduce factory
	Change method signature
	Transform module to package
	Encapsulate field
	Replace method with method object

It also can:

    Extract similar statements in extract refactorings
    Fix imports when needed
    Preview refactorings
    Undo/redo refactorings
    Interrupt refactorings
    Perform cross-project refactorings
    Handle basic implicit interfaces in rename and change signature
    Support Mercurial, GIT, Darcs and SVN in refactorings

%And helps IDE's with:

 %   Auto-completion
  %  Finding definition location
   % Getting pydoc
    %Finding occurrences
    %Organizing imports (removing unused and duplicate imports and sorting them)
    %Generating python elements

 %(the PyRefactor a plugin for sublime text 3 that uses Rope https://packagecontrol.io/packages/PyRefactor)

 %It has a module that tries to support build-in types and functions.
